%                                                                 aa.dem
% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style
%
\documentclass{aa}  

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[usenames, dvipsnames]{color}
\usepackage{overpic} % add text to fig


% NOTATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hls}{HLS\,J0918+5142}
\newcommand{\ftone}{f_{\rm{tone}}}
\newcommand{\am}{x}
\newcommand{\elev}{\delta}
\newcommand{\nika}{NIKA2}
\newcommand{\aka}{a.\,k.\,a.}
\newcommand{\wrt}{w.\,r.\,t.}
\newcommand{\bm}{{\tt beammap}}
\newcommand{\bms}{{\tt beammaps}}
\newcommand{\rf}{\emph{RfdIdQ}}
\newcommand{\kidpar}{\emph{kidpar}}
\newcommand{\radec}{\emph{R.\,A.,\,Dec}}
\newcommand{\cm}{\emph{common~mode}}
\newcommand{\cmoneb}{\emph{common~mode~one~block}}
\newcommand{\afternoon}{temperature-induced}
\newcommand{\Afternoon}{Temperature-induced}

% COMMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\todo}[1]{ {\color{magenta} $[$ TO DO: $]$ #1} }


\begin{document} 


   \title{NIKA2 Calibration and Performance at the IRAM 30-m Telescope}

   \author{Laurence Perotto
     \inst{1}
     \and
     Others ToBeDiscussed
%     Nicolas Ponthieu
%     \inst{2}
%     \and Juan-F. Mac\'ias-P\'erez
%     \inst{1}
%     \and 
%     F.-Xavier D\'esert
%     \inst{2}
%     \and 
%     Jean-Fran\c cois Lestrade
%     \inst{3}
%     \and
%     Herv\'e Aussel
%     \inst{4}
%     \and
%     Fr\'ed\'eric Mayet
%     \inst{1}
%     \and
%     Florian Ruppin
%     \inst{1}
     \and
     NIKA2 CORE TEAM
   }

   \institute{Univ. Grenoble Alpes, CNRS, Grenoble INP, LPSC-IN2P3, 53, avenue des Martyrs, F-38000 Grenoble, France \\
     \email{laurence.perotto@lpsc.in2p3.fr}
    % \and
    % Univ. Grenoble Alpes, CNRS, IPAG, F-38000 Grenoble, France\\
    % \and
    % LERMA, Observatoire de Paris, PSL Research University, CNRS, Sorbonne Universités, UPMC Univ. Paris 06, F-75014, Paris, France\\
    % \and
    % AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France
   }

   \date{Received April XX, 2019; Accepted XXXX XX, 2019}

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory
   
   \abstract
   % context heading (optional)
   % {} leave it empty if necessary  
       {The New IRAM KID Array, NIKA2, is a dual-band millimetric
         camera of thousands of Kinetic
         Inductance Detectors (KID) installed at the IRAM 30-meter
         telescope at Pico Veleta (Spain). The instrument
         commissioning  was successfully completed in September
         2017. NIKA2 is now open to the scientific community and will
         operate for the next decade. NIKA2 will be a key experiment for a vast variety of
         astrophysic and cosmology purposes, including planet
         formation, star formation in the Milky Way, gas in
         nearby galaxies, galaxy formation at high redshift and
         cosmology with galaxy clusters. The success of this ambitious science
         program will depend on the accuracy of the calibration and
         its stability againts observing conditions.}
       % aims heading (mandatory)
       {We present the methods that have been developped for NIKA2
         calibration and their application to the first year of final
         set-up operation to assess the on-sky performance.}
       % methods heading (mandatory)
       {We used several
         thousands of observation scans that were acquired at the February
         2017 technical campaign, during which NIKA2 instrumental set-up was
         in the final configuration for the first time,
         and at the first science pools that took place in October 2017 and
         January 2018. This vast data set allows us to check the performance
         stability for one year and against a large range of observing
         elevations and atmospheric conditions. %The calibration and
         %performance assessment methods that we have developed are also
         %thoroughly described, as well as the robustness tests that we have
         %performed.
       }
       % results heading (mandatory)
       {We find an average fraction of usable detectors during a
         typical observing scan of 84 per cent in the 260~GHz bands and 90 per cent in the
         150~GHz, which well cover the 6.5 arcmin diameter field of
         view. The beam pattern has been measured and is characterized
         by a full width at half maximum (FWHM) of $11.1\pm0.1$ arcsec
         and $17.6 \pm 0.1$, and a beam efficiency of $55\pm 3$ and
         $77\pm 2$ per cent at 260 and 150~GHz respectively. The
         statistital relative calibration uncertainties are of about 6
       and 3 per cent for these two frequency bands, which validates
       the accuracy of the method we have deployed to correct for the
       atmosphere attenuation. The top-of-atmosphere noise equivalent
       flux density (NEFD) at 260 and 150~GHz are of $30 \pm 3$ and
       $9 \pm 1$ mJy.s$^{1/2}$/beam. This state-of-the-art performance
       confers NIKA2 with excellent mapping capabilities characterized
       by mapping speeds of about 100 and 1400
       arcmin$^2$/hours/mJy$^2$ at 260 and 150~GHz.}
       % conclusions heading (optional), leave it empty if necessary 
       {}

   \keywords{Submillimeter, Photometry, Method: observational, Cosmology: Cosmic Microwave Background}

   \maketitle

   
%----------------------------------------------------------------------------------------
%	1./ INTRODUCTION
%----------------------------------------------------------------------------------------
\section{Introduction}
\label{se:intro}
\input{Introduction.tex}


%----------------------------------------------------------------------------------------
%	2./ INSTRUMENT
%----------------------------------------------------------------------------------------
\section{General view of the instrument}
\label{se:instru}
\input{Instrument.tex}


%----------------------------------------------------------------------------------------
%	3./ Observing mode
%----------------------------------------------------------------------------------------
\section{Observations}
\label{se:observations}
\input{Observations.tex}


%----------------------------------------------------------------------------------------
%	4./ Data reduction
%----------------------------------------------------------------------------------------
\section{Data Reduction}
\label{se:dataproc}
\input{Pipeline.tex}

%----------------------------------------------------------------------------------------
%	5./ Focal Plane Geometry
%----------------------------------------------------------------------------------------
\section{Focal Plane Reconstruction}
\label{se:geometry}
\input{FOV_Geometry.tex}

%----------------------------------------------------------------------------------------
%	6./ Beam Pattern
%----------------------------------------------------------------------------------------
\section{Beam Pattern}
\label{se:beam}
\input{Beam.tex}

%----------------------------------------------------------------------------------------
%	7./ Opacity derivation
%----------------------------------------------------------------------------------------
\section{Atmospheric opacity}
\label{se:opacity}
\input{Opacity.tex}

%----------------------------------------------------------------------------------------
%	8./ Calibration
%----------------------------------------------------------------------------------------
\section{Calibration}
\label{se:calibration}
\input{Calibration_1.tex}
\input{Calibration_2.tex}

%----------------------------------------------------------------------------------------
%	9./ Photometry&Stability
%----------------------------------------------------------------------------------------
\section{Photometry \& Stability Assessment}
\label{se:photometry}
\input{Photometry.tex}

%----------------------------------------------------------------------------------------
%	10./ Sensitivity
%----------------------------------------------------------------------------------------
\section{Sensitivity}
\label{se:sensitivity}
%\input{Sensitivity.tex}


%  CONCLU
%-------------------------------------------------------------------
\section{Conclusions}

The main measured parameters that define the measured NIKA2 performance
are gathered in Table~\ref{tab:nika2summary}.

\begin{table*}[!thbp]
  \caption[Main performance measurements]{Summary of the main characteristics describing the measured 
    performances of NIKA2.}
  \label{tab:nika2summary}
  \centering    
  \begin{tabular}{|r|c|c|c|c|l|}
    \hline\hline
    & Array 1 & Array 3  & Array 1\&3 & Array 2 & Reference \\
    \hline
    Reference Wavelength  [mm]  &  1.15    &  1.15   & 1.15  & 2.00   &   \\
    Reference Frequency  [GHz]  &  260    &  260   & 260  & 150   &  Sect.~\ref{se:photometric_system}  \\
    Central Frequency [GHz]     &  255.5  &  257.8 &      & 151.6 &  Sect.~\ref{se:bandpasses}  \\
    Bandwidth         [GHz]     &  47.8   &  45.7  &      & 42.1  &   \\
    \hline
    Number of designed detectors                   & 1140      &  1140    &    &    616  & Sect.~\ref{se:array}\\
    Number of valid detectors                      &  952      &   961    &    &    553  & Sect.~\ref{se:fov_geometry}\\
    Fraction of valid detectors [$\%$]             &  84       &   84     &    &     90  & \\
    %%% I find this number useless and misleading FXD 30 nov 2018
    %%% Effective FOV\tnote{a}\hspace{1mm} [arcmin]    &  5.7      &   5.7    &    &    5.9  & Sect.~\ref{se:grid_distortion}\\
    % Here I put the measured value (the modeled values are in the the field-of-view section) FXD
    Pixel size in beam sampling unit\tablefootmark{a}\hspace{3mm} [$F\lambda$] & 1.11 & 1.10  &  &  0.87 & Sect.~\ref{se:grid_distortion} \\
    \hline
    FWHM\tablefootmark{b}\hspace{3mm} [arcsec]    &  $11.1 \pm 0.2$   &  $11.0 \pm 0.2$  &   $11.1 \pm 0.1$  &  $17.6 \pm 0.1$  &  Sect.~\ref{se:mainbeam}\\
    Beam efficiency\tablefootmark{c}\hspace{3mm} [$\%$] &  $55 \pm 3$  &  $56 \pm 3$   &  $55 \pm 3$   &  $77 \pm 2$  &  Sect.~\ref{se:beam_efficiency}\\
    Relative rms FWHM on the FOV [$\%$]          &    6         &      6        &       6        &      3        & Sect.~\ref{se:fwhm_fov}\\
    \hline
    Reference FWHM\tablefootmark{d}\hspace{3mm} [arcsec]          &  $12.5$   &  $12.5$  &   $12.5$  &   $18.5$  &  Sect.~\ref{se:photometric_system}\\
    Reference Beam efficiency\tablefootmark{e}\hspace{3mm}  [\% ] & $70 \pm 4$ & $72 \pm 4$ & $70 \pm 4$ & $85 \pm 3$ &  Sect.~\ref{se:extended_source_calib}\\
    \hline
    rms pointing error    [arcsec]             & \multicolumn{4}{|c|}{$<3$} &  Sect.~\ref{se:pointing} \\
    \hline
    Absolute calibration uncertainty [\%]      &  \multicolumn{4}{|c|}{5}   & Sect.~\ref{se:ref_flux_uranus_neptune} \\
    \hline
    relative rms calibration error [\%]                 &    5.5       &     6.0       &      5.7       &     3.0       & Sect.~\ref{se:photometry_baseline} \\
    \hline
    $\alpha$ noise integration in time\tablefootmark{f}\hspace{3mm}  & 0.5  & 0.5  &  0.5 & 0.5 & Sect.~\ref{se:nefd_m1} \\
    \hline
    NEFD\small{(0mm, 90deg)}\tablefootmark{g}\hspace{3mm} [$\rm{mJy} \cdot \rm{s}^{1/2}/\rm{beam}$]  & $47 \pm 4$ & $38 \pm 3$  & $30 \pm 3$  & $9 \pm 1$ & Sect.~\ref{se:nefd_estimation_methods}\\
    NEFD\small{(2mm, 60deg)}\tablefootmark{h}\hspace{3mm} [$\rm{mJy} \cdot \rm{s}^{1/2}/\rm{beam}$]  & $57 \pm 5$ & $46 \pm 4$  & $36 \pm 3$  & $10 \pm 1$ & \\
    M$_{\rm{s}}$\small{(0mm, 90deg)}\tablefootmark{i}\hspace{3mm} [arcmin$^2$/h/mJy$^2$] & 45  & 70  & 111  &  1388 &  \\
    M$_{\rm{s}}$\small{(2mm, 60deg)}\tablefootmark{j}\hspace{3mm} [arcmin$^2$/h/mJy$^2$] & 31  & 48  &  77  &  1119 &  \\
    \hline
  \end{tabular}
  \tablefoot{ \\
    \tablefoottext{a}{Calculated from real array pixel size [2.75 mm / 2.0 mm] and unvignetted entrance pupil diameter [27m]}
    \tablefoottext{b}{Full-width at half-maximum of the main beam using the combined results of the three methods}
    \tablefoottext{c}{Ratio between the main beam power and the total beam power up to a radius of 180 arcsec}
    \tablefoottext{d}{Full-width at half-maximum of the beam used in our reference photometric system}
    \tablefoottext{e}{Ratio between the reference FWHM beam power and the total beam power up to a radius of 180 arcsec} 
    \tablefoottext{f}{Effective power law of noise reduction with integration time}
    \tablefoottext{g}{NEFD extrapolated at zero opacity}
    \tablefoottext{h}{NEFD in typical IRAM good sky opacity condition: 2mm pwv, $60^o$ elevation}
    \tablefoottext{i}{Mapping speed at zero opacity}
    \tablefoottext{j}{Mapping speed in typical IRAM good sky opacity condition: 2mm pwv, $60^o$ elevation}
  }
\end{table*}


\begin{enumerate}
\item \emph{FOV reconstruction}: All the designed KIDs detect the signal at least in some observation
  scans. We conservatively retain only the most stable KIDs, which are
  immune to the cross-talking effect and yield good signal-to-noise
  measurement. We defined 'valid' KIDs as the detectors that have been
  retained in at least two independent KID selections, as discussed in
  Sect.~\ref{se:fov_geometry}. We report valid KID fractions of $84\%$
  for the $1\,\rm{mm}$ channel arrays and $90\%$ for Array 2. The other
  KIDs, which do not meet the validity criterion, are ramdomly
  distributed across the FoV, so that the whole $6.6\,\rm{arcmin}$ FoV is
  covered. Considering the designed KID grid as discussed in
  Sect.~\ref{se:grid_distortion}, the distance between
  neighbour KIDs is $9.8''$, $9.7''$ and $13.3''$ for Array 1, 3 and 2
  respectively, which defined an occupation surface per KID. The area
  covered by all KIDs is in turn associated to a measured total FoV of
  $6.6$~arcmin diameter for each array.
  %The surface
  %covered by all valid KID is in turn associated to an effective FoV of
  %$5.7'$ for Array 1$\&$3 and of $5.9'$ for Array 2.       
  %gs   = [9.8, 9.7, 13.3] ;; gridstep in arcsec
  %ndet = [952, 961, 553]
  %print, sqrt((ndet*(gs/60.0)^2)/!dpi*4.0)
  %% F\lambda = gridstep\times D(30m)/\lambda
  
\item \emph{Beam Properties:} While the full beam pattern presents a complexe structure as discussed
  in Sect.~\ref{se:fullbeam}, the main beam is well described with a 2D
  Gaussian of FWHM of $11''$ for the $1\,\rm{mm}$ channel arrays
  and $17.6''$ for Array 2, with uncertainties of  $0.2''$ for the
  combination of Array 1$\&$3 and for Array 2, as presented in
  Sect.~\ref{se:fwhm_results}.
  Comparing the main beam fit to the measured full beam, we derive the
  main beam efficiency up to a radius of $180''$. We find beam
  efficiencies of $55 \pm 3 \%$ at $1\,\rm{mm}$ and $77 \pm 2 \%$ at
  $2\,\rm{mm}$. %These meet the expectations for an instrument that does not
  %resort to feed horns.
  The chosen $180''$ cutting radius ensures an accurate
  measure of the beam patterning using a single \bm\ scan. However,
  dedicated studies based on the Lunar edge observations showed that
  a sizable fraction of the full beam stems from beyond this
  radius. This fraction is about $35\%$ at $1\,\rm{mm}$ and about $20\%$
  at $2\,\rm{mm}$ (using Kramer et al 2013). Using individual map per
  KID, we evaluate the rms dispersion of the main beam FWHM across the
  FoV, as discussed in Sect.~\ref{se:fwhm_fov}. We measured rms
  dispersions of about $0.6''$ at both wavelengths using N2R9 data. These
  constitute a conservative estimate since the rms dispersion has been
  further improved by optimizing the telescope focus settings from N2R12
  on.  

  % calib
\item \emph{Calibration uncertainties:} We evaluated the statistical calibration uncertainties using 264 
  scans of sources, whose flux density is above about one Jy/beam,
  acquired during N2R9, N2R12 and N2R14, and selected on the observing UT hour basis, as discussed in
  Sect.~\ref{se:photometry_baseline}. We find rms calibration
  uncertainties of about $6\%$ at $1\,\rm{mm}$ and about $3\%$ at
  $2\,\rm{mm}$, which are state-of-the-art performance for instrument
  operated at these wavelengths. 
  

  % noise&sensitivity
\item \emph{Sensitivity:} The noise well integrates as the square root of the integration time
  for series of scans acquired in similar observing conditions as
  discussed in Sect.~\ref{se:nefd_m1}. The NEFD estimates reported in
  Table~\ref{tab:nika2summary} are based on more than one thousand scans
  acquired during N2R9, N2R12 and N2R14, and thus constitute
  conservative estimates that encompass a large range of observing
  conditions, as addressed in Sect.~\ref{se:nefd_scatter}. However,
  better NEFD have been found using homogeneous series of about one
  hundred scans of e.g. \hls\, as reported in
  Table~\ref{tab:nefd_summary}.  The conservative NEFD estimate reaches
  the goal value at $2\,\rm{mm}$. However, it is measured as slightly
  above the specifications at $1\,\rm{mm}$.
%\new{We have identified several areas of improvement that will make NIKA2
%more sensitive at 1~mm: 1)~change the dichroic element (one of
%the 1~mm polarization components (A1) is absorbed more than the other (A3)
%with the present dichroic), 2)~improve the data processing and in
%particular the noise decorrelation methods, 3)~upgrade the 1~mm
%arrays, 4)~increase the bandwidth of the 1~mm arrays, and 5)~upgrade
%the surface of the telescope.}
  NIKA2 mapping capabilities are better estimated by evaluating the
  mapping speed, which is defined as the sky area that is covered in one
  hour of observation to a noise level of $1\,\rm{mJy}$. NIKA2 mapping
  speed is an order of magnitude better than the previous generation of
  the IRAM $30\,\rm{mm}$ resident instruments. 
\end{enumerate}

\subsection*{Future plans}
The instrumental sensitivity at $1\,\rm{mm}$ is at present mainly
limited by the non-optimised transmission of the air-gap dichroic,
mostly prominent in one polarisation (A1) but affecting the other
(A3) as well. Actions are on-going to produce and test new
hot-pressed dichroics. We warn however that this task is far from
trivial.
Further possible areas of improvements for the $1\,\rm{mm}$
observation channel are: 1) improve the data processing and in
particular the noise decorrelation methods, 2) increase the
bandwidth of the $1\,\rm{mm}$ mm arrays (subjected to the
improvement of the dichroic) and 3) upgrade the surface of the
telescope.
  

 
\begin{acknowledgements}
     
\end{acknowledgements}

% WARNING
%-------------------------------------------------------------------
% Please note that we have included the references to the file aa.dem in
% order to compile it, but we ask you to:
%
% - use BibTeX with the regular commands:
\bibliographystyle{bibtex/aa} % style aa.bst
\bibliography{bibtex/NIKA2_biblio} % your references Yourfile.bib
%
% - join the .bib files when you upload your source files
%-------------------------------------------------------------------

\begin{appendix}
  \section{Reference flux density of the calibrators}
  \label{se:ref_flux_calibrator}
  \input{calibrator_flux_model.tex}
  
  \section{Reconstruction of the focus surfaces}
  \label{sec:focus_surfaces}
  \input{Focus_surfaces.tex}

  \section{Photometric correction}
  \label{se:photometric_correction}
  \input{photometric_correction.tex}
\end{appendix}
%
%
\end{document}
