


\subsection{Data selection}% {\color{YellowGreen} Laurence}}
\label{se:data_selection}

For calibration and performance assessment, we select scans in average
observing conditions by performing mild selection cuts. These scan
cuts rely on zenith opacity estimates in NIKA2 bands $\tau$, as
described in Sect.~\ref{se:opacities}, and on the observation date
conditions where:
%
\begin{itemize}
\item[i)] $\tau_{3} < 0.5$, where $\tau_{3}$ is the $\tau$ estimate for
  Array 3, corresponding to a decrease of the signal by a factor of
  two at $45^{o}$ of elevation;
\item[ii)] $x\, \tau_{3} < 0.7$ and $\elev > 20^{o}$, where $\elev$ is the
  elevation of the telescope and $x$ the
  air mass, which depends on the elevation as $x=(\sin{\elev})^{-1}$. This
  threshold corresponds to a decrease of the signal by a factor of two;
\item[iii)] observation date from 22:00 to 9:00 UT and from 10:00 to
  15:00, that is excluding the sunrise period and the late afternoon.
\end{itemize}
%
As discussed in Sect.~\ref{se:obsdate_variations}, the late afternoon
observation are \new{often affected by time-variable broadening of the
  telescope beams caused by (partial) solar irradiation of the primary
  mirror and/or anomalous atmospheric refraction.}
Around sunrise, the focus shifts continuously due to the ambient temperature
change until the temperature stabilizes, so that the scans taken from
9:00 to 10:00 UT are likely not to be optimally focused.
After the focus stabilisation, morning period 
from 10:00 to 15:00 UT offers stable observing conditions
if the telescope is not heated due to observations in a
direction close to the Sun. Otherwise, further scan selection based \new{on
the exact sequence of observations and on beam monitoring} might be needed before using these
observations for performance assessment.

   
In addition to the above scan selection cuts, we use a Gaussian beam
size criterion for the absolute calibration on planets
(e.g. Uranus). Namely, the FWHM estimated from the planet observation
map is asked to be lower than $12.5''$ at $1\,\rm{mm}$ and lower than $18''$ at
$2\,\rm{mm}$. In further mitigating the flux scatter due to beam broadening, we
ensure better accuracy of the absolute calibration.  
%, which correspond to a beam about $15\%$ larger than the average
%beam (see Sect.~\ref{se:beams}). The rational of this extra cut is
%mitigating the flux scatter due to beam broadening, and thus
%preserving the absolute calibration accuracy, as discussed in
%Sect.~\ref{se:calibration}.




