
NIKA2 photometric capabilities after the calibration presented in
Chapter~\ref{se:calibration}, are assessed in this section. Firstly,
we use observation of secondary calibrators (planetary nebulae NGC7027, CRL2688, and
MWC349A) to test the consistency of the flux density estimates with
expectations. Then, we verify the stability of the photometry with
respect to the atmospheric conditions using a large amount of
observations toward a large variety of sources. 


The methodology to evaluate the photometric
capabilities and calibration results are further described in
Sect.~\ref{se:photometry_criteria}.
%, which we recall
%comprizes the opacity correction as described in
%Sect.~\ref{se:opacity_correction}, the KID inter-calibration as discussed in
%Sect.~\ref{se:intercalibration} and the absolute calibration as
%addressed in Sect.~\ref{se:calibration}, are assessed in this section. First, we check that  
%secondary calibrators (planetary nebulae NGC7027, CRL2688, and
%MWC349A) %the two largest asteroids Ceres and Vesta were also
%observed.
In Sect.~\ref{se:ref_flux_secondaries}, the flux density expectations
in NIKA2 bands for the considered secondary calibrators are
determined. Then, we evaluate both the calibrator measured-to-expected
flux density ratio and the calibration statistical errors for the
baseline calibration method in Sect.~\ref{se:photometry_baseline}. 
In Sect.~\ref{se:photometry_others}, we compare these results with other
calibration method results. 
%Finally, in Sect.~\ref{se:aperture_photometry}, we check the robustness of the calibration
%results using an alternative calibration method that relies on
%aperture photometry.

\section{Calibration validation criteria}% {\color{LimeGreen} Laurence}}
\label{se:photometry_criteria}

\subsection{Calibration bias}
The calibration accuracy is primarily assessed by checking
that the flux density measurement of known sources is unbiased.

This performance test also depends on the accuracy with which the
chosen secondary calibrator SED is known. Our main secondary
calibrator is MWC349, for which we have derived precise NIKA2 flux
density espectations as discussed in
Sect.~\ref{se:ref_flux_secondaries}.
These are mainly limited by the absolute calibration of the Plateau de
Bure interferometer and VLA~\cite{krips}.

We define the calibration bias $b_{A_i}$ per array or array combination as
the ratio between the measured flux density $\hat{S}_{A_i}$ using the
fixed-width Gaussian beam photometry as discussed in
Sect.~\ref{se:flux_density_equation} and the flux density expectations $S^{0}_{A_i}$ as
given in Sect.~\ref{se:ref_flux_secondaries}. From a series of
secondary calibrator scans, we evaluate the average calibration bias
$b_{A_i}$, which by construction, should be equal to
unity within the precision with which the expected flux densities are
known. Moreover, the calibration bias stability against the observed
opacity provides us with a robustness test of the opacity correction,
and the stability againts the measured beam size, a test of the
photometric susceptibility to optical variations.
%(driven by the main dish distortions)

\subsection{Calibration stability}

The stability of the measured flux densities with respect to the observing
conditions is tested using a large amount of observation scans toward
various sources.

\samu{As the flux density of most of these sources is unknown a priori, we
compare the flux density estimate in a single observation scan to the
average flux density thorough an observation campaign. This method
requires the selection of sources that are bright enought to be detected with a high
signal-to-noise ratio with a single repetition of an usual
$8'\times 5'$ OTF raster scan. Namely, we perform a source
selection by thresholding the flux estimate to $800~\rm{mJy}$ at
$1~\rm{mm}$ and $400~\rm{mJy}$ at $2~\rm{mm}$. Moreover, we consider
only the sources for which a minimum of $10$ scans are available after
selection to ensure a precise average flux density
estimation. Finally, the selected source scans must meet the baseline
selection criteria.}

We evaluate the standard deviation of the bright source measured-to-median flux
density ratio $\sigma_{A_i}$, where $A_i$ stands for Array 1, 2, 3
and the $1\,\rm{mm}$ array combination. 
This quantity constitutes an estimate of the statistical calibration
uncertainties that encloses errors of optical, atmospheric, noise and
data processing origins.
Added in quadrature with the model uncertainties on the primary
calibrator flux density expectations reported
in~\cite{Morenothesis},~\cite{bendo2013} and with the bandpass
uncertainties, it represents a
conservative estimate of the total absolute calibration errors.
