%
%%
%%
%%

%% LP: first synthetic version of Appendix D. 

%% LP modif : to be validated by HA :
%% - 'spectral irradiance' remplac\'ee par 'flux density', qu'on utilise plus souvent
%% - 'response' remplac\'e par 'map' [ une occurence]
%% - '\Omega_{b}' remplac\'e par 'B_{k}', plus \'evocateur du beam et souligne la dependance dans le KID k
%% - '\Omega_{s}' remplac\'e par '\Omega_{p}' pour \'evoquer angle solide sur la pupille
%% - A VERIFIER: les quantit\'es pas connues précisement
%%   'Because both $A_{p}$ and $ \Omega_{p} $ are not known with good accuracy', correct ? 



%% [intro]
The calibration of the NIKA2 instrument in its final configuration of
January 24th 2017 is studied in this section in using Uranus as the
main primary calibrator. Neptune and Mars are also considered as
valluable alternatives to calibrate when Uranus is not visible.

% HA 
\subsection{Photometric System}
\label{se:cal_HA}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
     & 1 mm & 2 mm \\
\hline
Reference frequency $\nu_{0}$ & 260 GHz & 150 GHz \\
\hline
Reference FWHM                      & 12.5  '' & 18.5 '' \\
\hline
\end{tabular}
\caption{NIKA2 reference frequencies and FWHM}
\end{center}
\label{tab:definitions}
\end{table}

\subsubsection{Main photometric equation}

Starting from the general equation for the response of a detector to
an astronomical source, we derive the main photometric equation as
detailed in Sect.~\ref{ap:cal_HA}.
The map (in units of the KID resonance frequency shift or $\rm Hz$) of a source using a single KID $k$
after correction of the atmospheric absorption is
\begin{equation}
R_{k}(\theta, \phi) \simeq G_{k}  A_{p}\Omega_{p} \int_{0}^{+\infty} I(\nu)
T(\nu) T_{atm}(\nu) B_{k} (\theta, \phi, \nu)  d\nu 
\label{eq:mainphot}
\end{equation}

where we have considered a source observed at airmass $\am$ under
$mm_{H_{2}O}$ of precipitable water, with specific intensity $I_{\nu}$ (in units
of  ${\rm W/m^{2}/sr/Hz}$) in the direction $\theta, \phi$, where $\theta$
is the off-axis distance and $\phi$ the position angle, illuminating the KID $k$. 
The dependance on elevation and opacity is corrected, as discussed in
section~\ref{se:opacities}, so that Eq.~\ref{eq:mainphot} is the KID
response outside of atmosphere (in terms of airmass, but not in terms
of transmission).

The integral in the right-hand part of Eq.~\ref{eq:mainphot} gives the total power (units of $\rm W$)
falling on the KID, where the factors are:
\begin{itemize}
\item $T(\nu)$, NIKA2 bandpasses, which are measured and corrected for the Raighleigh-Jeans term as discussed in Sect.~\ref{se:bandpasses}
\item $T_{atm}(\nu)$, the transmission of the atmosphere at zenith. 
\item $B_{k} (\theta, \phi, \nu)$, the fraction of source signal illuminating the KID, that is the beam function.  
\end{itemize}

The gain of the KID $k$ $G_{k}$ (units of  $\rm Hz \cdot \rm W^{-1}$) converts the total power in $\rm W$
to the frequency shift in $\rm Hz$. $A_{p}$ is the area of the entrance pupil ({\it i.e.} the
dish collecting area), and $\Omega_{p}$ is the solid angle of the source seen from the
entrance pupil.

Because both $A_{p}$ and $ \Omega_{p} $ are not known with good
accuracy, it is not possible to compute all the terms of
Eq.~\ref{eq:mainphot} from first principles, and a practical way of
calibrating the system must be used: it is done by observing a primary
calibrator.


\subsubsection{Beammap of a calibrator}

A primary calibrator is a source whose flux density (or spectral irradiance) is
known. For NIKA2, we use two planets as primary calibrators, Uranus
and Neptune.


The specific intensity $I_{c}(\nu)$ of the
calibrator is:
\begin{equation}
I_{c}(\nu) =  \frac{S_{c}(\nu)}{\Omega_{p}} =\frac{ S_{c}
(\nu_{0})}{\Omega_{p}} f(\frac{\nu}{\nu_{0}})  
\end{equation}
Where $S_{c}(\nu)$ is the flux density of the calibrator (units
of $\rm W/m^{2}/Hz$ or Jy). We parametrize the source flux density
as a function of a reference frequency $\nu_{0}$ that we choose
arbitrarily to be: $\nu_{0} = 150$~GHz for the 2mm array and $\nu_{0}
= 260$~GHz for both 1mm arrays. 


The beam $B_{k}$ is further parametrized as a function
of the effective frequency as defined in eq~\ref{eq:nueff} of Sect.~\ref{ap:cal_HA},
considering that its frequency dependency is only due to the diffraction law,
hence a variation as $1/\nu$.

With this in hand, we can write the equation of a beam map using a
single KID with eq~\ref{eq:mainphot}. At each position ($\theta, \phi$)
on the beam map (in units of $\rm Hz$) we have:
\begin{equation}
R_{c}(\theta, \phi) =  G_{k} A_{p} S_{c} (\nu_{0})  \int_{0}^{+\infty}
f(\frac{\nu}{\nu_{0}}) B_{k}(\nu_{0}, \theta \times \frac{\nu}{\nu_{0}},
\phi) T(\nu) T_{atm}(\nu) d\nu
\label{eq:beammap}
\end{equation}

\subsubsection{Calibration in FWHM$_{0}$ beam}

This map is fitted with a Gaussian of fixed width FWHM$_{0}$ (we
recall that $2 \sqrt{2\ln{2}} \sigma_{0} =  {\rm FWHM}_{0}$).
\begin{equation} 
R_{c}(\theta, \phi) = \frac{A_{c}}{2 \pi \sigma_{o}^{2}}
e^{-\frac{\theta^{2}}{2\sigma_{0}^{2}}}  + \epsilon(\theta, \phi)
\end{equation}
where $\epsilon(\theta, \phi)$ are the residuals of the fit.

Assuming that the fit is not biased, we have:
\begin{equation} 
\int\int R_{c}(\theta, \phi) \sin \theta d\theta d\phi = A_{c}
\end{equation}
because errors average out so that:
\begin{equation} 
\int\int \epsilon (\theta, \phi) \sin \theta d\theta d\phi = 0
\end{equation}
But we also know that integral of the beammap should give the power
emitted by the source. Therefore, we form the map:
\begin{equation}
M_{c}(\theta, \phi) = R_{c}(\theta, \phi)   S_{c} (\nu_{0}) / A_{c}
\end{equation}
where  $S_{c} (\nu_{0})$ is the spectral irradiance of the calibrator
at a reference frequency $\nu_{0}$ given in
table~\ref{tab:definitions}. This map has units of $\rm W/m^{2}/Hz$. Note
that the choice of the reference frequency is arbitrary, it is a
convention. By construction, integrating over the map we have:

\begin{equation}
\int\int M_{c}(\theta, \phi) \sin \theta d\theta d\phi = S_{c}(\nu_{0})
\end{equation}


Similarly, a point source with spectral irradiance $S_{s}(\nu)$ will
generate a response at position $(\theta, \phi)$
\begin{equation}
R_{s}(\theta, \phi) =  G_{k} A_{p}  \int_{0}^{+\infty}
S_{s}(\nu) B_{k}(\nu_{0}, \theta \times \frac{\nu}{\nu_{0}},
\phi) T(\nu) T_{atm}(\nu) d\nu
\end{equation}
Note here that the effective frequency for the beam is not necessarily
the same as the one for the primary calibrator, as it depends on the
source spectrum.


This beammap will be fitted with a gaussian of fixed width:
\begin{equation} 
R_{s}(\theta, \phi)  = \frac{A_{s}}{2 \pi \sigma_{o}^{2}}
e^{-\frac{\theta^{2}}{2\sigma_{0}^{2}}}  + \epsilon(\theta, \phi)
\end{equation}

The quoted flux for the source is then:
\begin{equation}
S_{q}(\nu_{0}) =  S_{c} (\nu_{0})  \times \frac{A_{s}}{A_{c}}
\end{equation}

In other words, the quoted flux is the flux that should have the
calibrator in order to generate a response that would be fitted with a
gaussian of fixed width and the same amplitude as the source.
Let us form the map:

\begin{equation}
M_{s}(\theta, \phi) = R_{s}(\theta, \phi)   S_{c} (\nu_{0}) / A_{c}
\end{equation}

 {\em The map $M_{\theta, \phi}$ is said to be calibrated in Jy / FWHM$_{0}$ beam.}

If we have a single point source in M, we have when we fit a gaussian
of fixed width:
\begin{equation}
\int \int M_{s}(\theta, \phi) \sin \theta d\theta d\phi = A_{s}  S_{c} (\nu_{0}) /
A_{c} = S_{q}(\nu_{0})
\end{equation}


Note that the quoted flux {\em is not} the flux of the source at the
reference frequency. In order to find the flux of the source at the
reference frequency, a color correction has to be applied
\begin{equation}
S_{s}(\nu_{0}) = S_{q}(\nu_{0})  C_{s}
\end{equation}
The color correction $C_{s}$ is derived in Sect.~\ref{ap:cal_HA}. 


For aperture photometry, the map calibrated in Jy / $FWHM_{0}$ must be
converted in a map in Jy / pixel. 

